---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sdeshiny

Read this in other languages: [Español](README.es.md)

This package contains a [Shiny](https://shiny.rstudio.com/) application that works
as an interface to the packages [deSolve](https://CRAN.R-project.org/package=deSolve)
and [phaseR](https://CRAN.R-project.org/package=phaseR). This app was developed as 
a final proejct for a course on mathematical modelling taught by [Marco Scavino](https://scholar.google.com/citations?user=woT0slUAAAAJ)
on February 2020 in Rosario.

The goal of this app is to make it easier to solve system of differential equations
without having to write R code or knowing how to use packages deSolve/phaseR.

One of the nice features of this app is that the user can write autonomous system of 
differential equations using a `mathInput()` from the package [`shinymath`](https://github.com/tomicapretto/shinymath)
with arbitrary state and parameter names. Under the hood, the LaTeX representation
is translated to R code via [latex2r](https://github.com/tomicapretto/latex2r).

The app automatically recognizes states, parameters, and the independent variable of
the system. Then, the app shows the inputs that correspond to these components. 
What's more, the user not only gets graphics to analyze the ODE system but also the 
R code required to reproduce the analysis. Thus, this app also serves as a starting
point to those who don't know how to use packages deSolve and phaseR.

Finally, the app is now multi-lingual. It supports both Spanish and English.

## Installation

This package is not published on CRAN and it is not likely to happen in the near future.
The development version can be installed from [GitHub](https://github.com/) via:

``` r
# install.packages("devtools")
devtools::install_github("tomicapretto/sdeshiny")
```
## Running the app

You just need to call `launch_app()`

```{r example, eval=FALSE}
sdeshiny::launch_app()
```

## Notes

It is important to remark some characteristis and limitations of the system.

### `latex2r`

This app comes with all the limitations and characteristics from the parser implemented
in `latex2r`. Please have a look at [these notes](https://github.com/tomicapretto/latex2r#supported-latex) 
before using the app.

### Leibniz notation

The differential equations must be expressed using Leibniz notation.

Good:

* `dX/dt = -\lambda * X`

Bad:

`X' = -\lambda * X`

## Introductory video (in Spanish)

* [Como usar sdeshiny](https://www.youtube.com/watch?v=CZP9TaTwRlI)
